---
title: "Delirium, Depression and LTCI"
output:
  html_notebook:
    toc: yes
    toc_float: yes
    code_folding: hide
    theme: yeti
---

# Description of Project

In its early stages, this analysis aims to look at the relationship between a pre-admission history of depression in BRAIN-ICU patients, as reported by surrogates, vs outcomes in the hospital and at long-term followup.

Currently, we will look at pre-admission history of depression versus the following outcomes:

- Brain dysfunction during hospital admission, defined as days alive and free of delirium and coma (DCFDs) during the 14 days after study enrollment
- Global cognition after critical illness, defined by RBANS Global scores at 3 and 12 months after hospital discharge
- Severity of depression after critical illness, defined by Beck Depression Inventory (BDI)-II scores at 3 and 12 months after hospital discharge

All outcomes will be examined using multivariable regression, adjusting for potential confounders. Specific regression type and confounders will be detailed in each section.

```{r setup, message = FALSE, results = "hide"}
## Set default options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(width = 100)

## Load libraries
suppressPackageStartupMessages(library(huxtable))
suppressPackageStartupMessages(library(rms))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(forcats))
suppressPackageStartupMessages(library(naniar))
suppressPackageStartupMessages(library(sparkline))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(JTHelpers))

## Analysis data sets are stored in parent directory
load("..//braindata.Rdata")

## Data management:
## - Make frailty numeric; will be treated as continuous in models
## - Race will only be used in imputation, and our population is overwhelmingly
##   white; combine all non-white patients into one category
brain.oneobs <- brain.oneobs %>%
  mutate(
    frailty = as.numeric(substr(as.character(frailty), 1, 1)),
    race.wb = factor(ifelse(is.na(race.wb), NA,
                     ifelse(race.wb == "White", 1, 2)),
                     levels = 1:2, labels = c("White", "Non-White"))
  )

## Patients with this level of withdrawal have no data; they'll be excluded
wd_nodata <- c(
  "2. W/D from Participation and All Data Collected",
  "4. N/A Study Staff Withdrew Patient"
)

## Which variables will be modeled using restricted cubic splines in all
## analyses? Create a string to use for pattern matching with stringr later
rcs_vars <- c("age.enroll", "charlson.score", "stroke.risk", #"iqcode.score.e",
              "ses.score", "edu", "apache.aps", "mean.modsofa.icu", "del.s.imp",
              "coma.s.imp", "ints.sat.l90.s", "icudays.sevseptic.s",
              "bdi.totscore")

rcs_replace_regex <- paste0(
  "(",
  paste(
    paste0("^", str_replace_all(rcs_vars, fixed("."), fixed("\\.")), "$"),
    collapse = "|"
  ),
  ")"
)

## Which variables will be included in imputation as strictly linear?
lin_vars <- c("adl.e", "adl.totscore", "faq.e", "faq.totscore", "frailty",
              "frailty.fu", "iqcode.score.e", "edu", "bdi.totscore")

lin_replace_regex <- paste0(
  "(",
  paste(
    paste0("^", str_replace_all(lin_vars, fixed("."), fixed("\\.")), "$"),
    collapse = "|"
  ),
  ")"
)

## -- Function to make huxtable from rms_model_results() df + col headers ------
make_modresults_ht <- function(resultsdf){
  ht <- resultsdf %>%
    hux() %>%
    ## Align variable name to left, all other columns to right
    set_align(row = everywhere, col = everywhere, byrow = TRUE,
              value = c("left", rep("right", ncol(resultsdf) - 1))) %>%
    ## Set p-value column to three decimal places by default
    set_number_format(row = everywhere, col = 7, value = 3) %>%
    ## Bold column headers, add line after first row
    set_bold(row = 1, col = everywhere, TRUE) %>%
    set_bottom_border(row = 1, col = everywhere, value = 1) %>%
    ## Gray out all info except the row for history of depression, our main
    ## exposure of interest
    set_text_color(
      row = grep("^hx\\.depression$", resultsdf$label, invert = TRUE),
      col = everywhere,
      value = "#838383"
    ) %>%
    ## Table should take up 90% of document width
    set_width(0.9)
}

```

# Depression vs Delirium/Coma-Free Days during Hospitalization

```{r dcfd_prep, results = "hide"}
## -- Dataset for running DCFD models ------------------------------------------
## Variables involved in model
dcfd_vars <- c("hx.depression", "dcfd.14.imp", "age.enroll", "sex.pp",
               "charlson.score", "stroke.risk", "iqcode.score.e", "edu",
               "ses.score", "frailty", "apache.aps")

df_dcfds <- brain.oneobs %>%
  filter(is.na(studywd.amt) | !(studywd.amt %in% wd_nodata)) %>%
  ## Keep all variables involved in model, plus additional variables that may
  ## be helpful during imputation
  dplyr::select(id, one_of(dcfd_vars),
                adl.e, faq.e, bmi, race.wb, sofa, smoke, alcohol)

dd_dcfds <- datadist(df_dcfds)
options(datadist = "dd_dcfds")

## -- How much missingness is in DCFDs data? (Will we want to impute?) ---------
misstable_dcfds <- miss_var_summary(df_dcfds[, dcfd_vars]) %>%
  filter(percent > 0) %>%
  rename("Variable" = "variable", "N Missing" = n_missing, "% Missing" = percent)

missplot_dcfds <- gg_miss_var(df_dcfds[, dcfd_vars], show_pct = TRUE) +
  geom_hline(yintercept = 5, colour = "grey50", linetype = "dotted") +
  scale_y_continuous(name = "% Missing", limits = c(0, 100))

## -- Sparkline to show distribution of DCFDs ----------------------------------
dcfd_dist <- df_dcfds %>%
  filter(!is.na(dcfd.14.imp)) %>%
  group_by(dcfd.14.imp) %>%
  summarise(count = n())

spark_dcfds <- sparkline(
  dcfd_dist$count,
  type = 'bar',
  barColor = "#117cad",
  elementId = "sparkline-dcfds"
)

```

All `r nrow(subset(brain.oneobs, is.na(studywd.amt) | !(studywd.amt %in% wd_nodata)))` patients enrolled in BRAIN-ICU who did not completely withdraw from all participation are eligible for inclusion. Due to the bimodal distribution of delirium/coma-free days in our cohort `r spark_dcfds`, we will use a proportional odds logistic regression model, which will adjust for the following covariates measured at ICU admission:

- Age
- Gender
- Charlson
- Framingham stroke risk
- IQCODE
- Years of education
- AHRQ socioeconomic score
- CSHA frailty
- APACHE APS at enrollment

All continuous covariates are allowed to have a nonlinear relationship with DCFDs using restricted cubic splines with three knots.

## Missing Data

We quickly examine the amount of missing data in this cohort to see if multiple imputation might be advisable. A reference line at 5% missing is included; below this level, we typically aren't terribly concerned about missing data.

```{r dcfd_missing}
ggplotly(missplot_dcfds) %>%
  layout(title = "Missingness in DCFD Outcome Data",
         yaxis = list(title = ""),
         showlegend = FALSE)

```

Most covariates have very little missingness, but we do have more than a negligible number of patients missing AHRQ socioeconomic score. These patients are likely different from patients with SES score available, as SES score is usually missing on patients whose addresses are difficult to geocode (eg, very rural areas). In addition, our primary exposure of history of depression is missing on quite a few patients. Therefore, we'll use multiple imputation to reduce the possibility of bias in our results, using five imputations (with three burn-in imputations) and predictive mean matching.

```{r dcfd_model, results = "hide"}
## -- Multiple imputation using aregImpute() -----------------------------------
## Some variables have too little variability to use splines; replace these
## with I(var) for imputation formula
dcfd_areg_vars <- setdiff(names(df_dcfds), "id") %>%
  str_replace(lin_replace_regex, "I\\(\\1)")

dcfd_areg_form <- as.formula(
  paste("~", paste(dcfd_areg_vars, collapse = " + "))
)

set.seed(56)
dcfd_areg <- aregImpute(dcfd_areg_form, data = df_dcfds)

## -- Fit model ----------------------------------------------------------------
## Will use restricted cubic splines for nonlinear terms; replace most
## continuous variables' names with rcs(var, 3)
dcfd_mod_vars <- str_replace(dcfd_vars, rcs_replace_regex, "rcs\\(\\1, 3\\)")

dcfd_mod <- fit.mult.impute(
  as.formula(
    paste(
      "dcfd.14.imp ~", paste(setdiff(dcfd_mod_vars, "dcfd.14.imp"),
                             collapse = " + "
      )
    )
  ),
  data = df_dcfds,
  xtrans = dcfd_areg,
  fitter = lrm
)

dcfd_results <-
  rms_model_results(dcfd_mod, rndDigits = 2) %>%
  ## Remove long list of rows telling us how many patients have each DCFD value
  ## (refer to sparkline above for distribution)
  filter(is.na(as.numeric(label)))

## Add column names manually - couldn't get huxtable to do this properly/quickly
dcfd_results <- rbind(
  c("Variable", "Ref Level", "Comparison", "Odds Ratio (95% CI)",
    "X^2^", "df", "P"),
  dcfd_results
)

dcfd_ht <- make_modresults_ht(dcfd_results)

## Numbers for text statement
dcfd_or <- exp(coef(dcfd_mod)["hx.depression=Has history"])
dcfd_reduction <- 1 - (dcfd_or / 1)
dcfd_orci <- dcfd_results[grep("^hx\\.depression", dcfd_results$label), "est.ci"]

```

## Model Results

A pre-admission history of depression, as ascertained by surrogate questionnaire, has an odds ratio (95% confidence interval) vs DCFDs of `r dcfd_orci`; this indicates that, after adjusting for potential confounders, patients with a documented history of depression have on average `r round(dcfd_reduction * 100)`% `r ifelse(dcfd_or < 1, "lower", "higher")` odds of more "good" days alive and free of brain dysfunction. (Put simply, pre-admission history of depression is marginally associated with worse brain dysfunction and/or mortality in the hospital; **importantly**, we cannot tell from this analysis whether depression is associated mostly with delirium, coma, mortality, and/or some combination of the three.)

```{r dcfd_results, results = "asis"}
print_html(dcfd_ht)

```

# Depression vs Long-Term Outcomes

To examine the association of a reported pre-admission history of depression with long-term cognition and depression, we will use multivariable regression with history of depression as our primary exposure of interest and either RBANS global cognition scores or Beck Depression Inventory II (BDI-II) depression scores as our outcomes, using separate models for scores at 3 and 12 months after hospital discharge. All models will adjust for the following potential confounders, measured at ICU admission or summarized over the ICU course:

- Age at enrollment
- Gender
- Charlson comorbidity index
– Framingham Stroke Risk Profile
- IQCODE
- Years of education
- Apolipoprotein E genotype
- Mean modified SOFA score in the ICU ("modified" = GCS is not included)
- Days of delirium in the hospital
- Days of coma in the hospital
- Days of severe sepsis in the ICU
- Intervals where O2 saturations <90% in the ICU

Except for IQCODE (which has too little variability to allow splines), all continuous covariates will be allowed to have a nonlinear relationship with our outcome using restricted cubic splines with three knots.

In all long-term models, we'll include patients who had any assessment data available at a given time point (even if the outcome of interest is missing). This means that a) we'll have the same number of patients in RBANS and BDI models at a given time point, and b) we'll need to handle some missing outcome and covariate data using multiple imputation, particularly because there are likely to be differences between patients with and without outcome data available.

```{r ltoutcomes_prep, results = "hide"}
## -- Datasets for running long-term outcome models ----------------------------
## Patients will be included in long-term models at a given time point if they
## have *any* followup assessment data
lt_outcomes <- c("bdi.totscore", "bpi.intense", "bpi.inter", "pcl.totscore",
                 "caps.score", "mmse.tscore", "trail.a.tscore",
                 "trail.b.tscore", "rbans.immmemory.tscore",
                 "rbans.visuo.tscore", "rbans.language.tscore",
                 "rbans.attention.tscore", "rbans.delayedmem.tscore",
                 "rbans.global.score", "faq.totscore", "adl.totscore",
                 "sf36.pcs", "sf36.pcs")

## Indicator for whether patient had any of above at each followup time point
brain.fu$any_outcomes <- rowSums(!is.na(brain.fu[,lt_outcomes])) > 0

## Variables involved in LTCI models (same covariates for BDI, LTCI)
ltci_vars <- c("hx.depression", "rbans.global.score", "bdi.totscore",
               "age.enroll", "sex.pp", "e4.type", "edu", "iqcode.score.e",
               "charlson.score", "stroke.risk", "mean.modsofa.icu", "del.s.imp",
               "coma.s.imp", "ints.sat.l90.s", "icudays.sevseptic.s")

## Starting point data set for all long-term outcomes: merge variables from
## brain.oneobs onto brain.fu (this would be inefficient if our data were very
## large... but it's not)
df_lt_base <- brain.fu %>%
  dplyr::select(id, fu.period, any_outcomes, one_of(ltci_vars),
                adl.totscore, faq.totscore, frailty.fu) %>%
                ## Was going to include domains/Trails in imputation, but too
                ## many variables in was causing problems, and domains/Trails
                ## have comparable amounts of missingness and tend to be missing
                ## together, so we leave them out
                ## ggplot(data = df_lt_base,
                ##        aes(x = rbans.global.score, y = trail.b.tscore)) +
                ##   geom_miss_point(alpha = 0.05)
                # matches("^rbans\\..+\\.tscore$"),
                # matches("^trail\\.[a|b]\\.tscore$"),
                # sf36.pcs, sf36.mcs) %>%
  left_join(
    dplyr::select(
      brain.oneobs,
      id, one_of(ltci_vars), one_of(dcfd_vars), bmi, race.wb, smoke, alcohol
    ),
    by = "id"
  ) %>%
  mutate(frailty.fu = as.numeric(substr(as.character(frailty.fu), 1, 1))) %>%
  dplyr::select(-dcfd.14.imp)

## Create datasets for 3&12m models, keeping only pts w/ at least some asmt data
df_lt_3 <- df_lt_base %>%
  filter(fu.period == "3 Month" & any_outcomes) %>%
  dplyr::select(-fu.period, -any_outcomes)
df_lt_12 <- df_lt_base %>%
  filter(fu.period == "12 Month" & any_outcomes) %>%
  dplyr::select(-fu.period, -any_outcomes)

## Create a single datadist for long-term outcomes, keeping all patients who
## had assessment data at either time point
dd_lt <- df_lt_base %>%
  filter(fu.period %in% paste(c(3, 12), "Month") & any_outcomes) %>%
  datadist()

options(datadist = "dd_lt")

```

## Missing Data

We have `r nrow(df_lt_3)` patients included in our long-term models at 3 months, and `r nrow(df_lt_12)` patients included at 12 months. Below, we show the proportion of missingness for each variable included in long-term models by time point. A reference line at 5% missing is included; below this level, we typically aren't terribly concerned about missing data.

```{r ltci_missing}
## -- How much missingness is in LTCI data? (Will we want to impute?) ---------
## Create a single df with missingness for both time points
misstable_ltci <- df_lt_base %>%
  filter(fu.period %in% paste(c(3, 12), "Month") & any_outcomes) %>%
  mutate(fu.period = fct_relevel(as.character(fu.period), "3 Month")) %>%
  group_by(fu.period) %>%
  dplyr::select(one_of(ltci_vars)) %>%
  miss_var_summary()

## This code is modified from Nick Tierney's naniar package - function doesn't
## currently allow easy faceting (hmm, maybe I should make a PR at some point)
missplot_ltci <-
  ggplot(data = misstable_ltci,
         aes(x = stats::reorder(variable, percent), y = percent, colour = variable)) +
  facet_wrap(~ fu.period) +
  geom_bar(stat = "identity", position = "dodge", width = 0) +
  geom_point() +
  geom_hline(yintercept = 5, colour = "grey50", linetype = "dotted") +
  scale_y_continuous(name = "% Missing", limits = c(0, 100)) +
  coord_flip() +
  scale_color_discrete(guide = FALSE) +
  labs(x = "") +
  theme_minimal()

```

```{r ltci_missing_plot}
ggplotly(missplot_ltci) %>%
    layout(title = "Missingness in Long-Term Outcomes Data",
           yaxis = list(title = ""),
           showlegend = FALSE)

```

Many covariates have very little missingness, but we do have quite a few missing both our outcomes and important covariates, including our main exposure of pre-admission depression. These patients are likely different from patients with complete data; it is especially likely that there are differences between patients who had complete RBANS and BDI data and those who did not. Therefore, we'll use multiple imputation to reduce the possibility of bias in our results, including all patients with at least partial long-term outcomes data at a given time point. Specifically, we'll use five imputations (with three burn-in imputations) and predictive mean matching.

```{r lt_impute, results = "hide"}
## -- Imputation objects for RBANS, BDI models ---------------------------------
## -- (we can use the same aregImpute objects for both) ------------------------
## -- Multiple imputation using aregImpute() -----------------------------------

## Some variables have too little variability to use splines; replace these
## with I(var) for imputation formula
lt_areg_vars <-
  setdiff(names(df_lt_base), c("id", "fu.period", "any_outcomes")) %>%
  str_replace(lin_replace_regex, "I\\(\\1)")

lt_areg_form <- as.formula(paste("~", paste(lt_areg_vars, collapse = " + ")))

set.seed(56)
lt_areg_3 <- aregImpute(lt_areg_form, data = df_lt_3, nk = 3)
lt_areg_12 <- aregImpute(lt_areg_form, data = df_lt_12)

```

## Depression vs Global Cognition after Hospitalization

We know that RBANS global cognition scores are normally distributed, so we will use multivariable regression models for both 3- and 12-month followup to determine the association between a pre-admission reported history of depression and global cognition.

```{r rbans_models, results = "hide"}
## -- Fit model ----------------------------------------------------------------
## Will use restricted cubic splines for nonlinear terms; replace most
## continuous variables' names with rcs(var, 3)
rbans_mod_vars <- str_replace(ltci_vars, rcs_replace_regex, "rcs\\(\\1, 3\\)")

fit_rbans_mod <- function(df, aregobj){
  fit.mult.impute(
    as.formula(
      paste(
        "rbans.global.score ~",
        paste(setdiff(rbans_mod_vars, "rbans.global.score"), collapse = " + ")
      )
    ),
    data = df,
    xtrans = aregobj,
    fitter = ols
  )
}

rbans_mod_3 <- fit_rbans_mod(df = df_lt_3, aregobj = lt_areg_3)
rbans_mod_12 <- fit_rbans_mod(df = df_lt_12, aregobj = lt_areg_12)

rbans_results_3 <- rms_model_results(rbans_mod_3, rndDigits = 2)
rbans_results_12 <- rms_model_results(rbans_mod_12, rndDigits = 2)

## Add column names manually - couldn't get huxtable to do this properly/quickly
rbans_colnames <- c("Variable", "Ref Level", "Comparison", "Difference (95% CI)",
                    "X^2^", "df", "P")
rbans_results_3 <- rbind(rbans_colnames, rbans_results_3)
rbans_results_12 <- rbind(rbans_colnames, rbans_results_12)

## Make huxtables
rbans_ht_3 <- make_modresults_ht(rbans_results_3)
rbans_ht_12 <- make_modresults_ht(rbans_results_12)

## Numbers for text statement
rbans_diff_3 <- coef(rbans_mod_3)["hx.depression=Has history"]
rbans_diffci_3 <-
  rbans_results_3[grep("^hx\\.depression", rbans_results_3$label), "est.ci"]
rbans_diff_12 <- coef(rbans_mod_12)["hx.depression=Has history"]
rbans_diffci_12 <-
  rbans_results_12[grep("^hx\\.depression", rbans_results_12$label), "est.ci"]

```

### Model Results, 3M

Compared to patients with no documented history of depression, patients with a pre-admission history of depression as ascertained by surrogate questionnaire have, on average, a difference of `r rbans_diffci_3` points on the RBANS global cognition battery three months after hospital discharge. This indicates that in our cohort, after taking into account other available covariates, there is no meaningful difference in global cognition between survivors of critical illness with and without a pre-admission history of depression.

```{r rbans_results_3, results = "asis"}
print_html(rbans_ht_3)

```

### Model Results, 12M

Compared to patients with no documented history of depression, patients with a pre-admission history of depression as ascertained by surrogate questionnaire have, on average, a difference of `r rbans_diffci_12` points on the RBANS global cognition battery a year after discharge. This indicates that in our cohort, after taking into account other available covariates, there is no meaningful difference in global cognition between survivors of critical illness with and without a pre-admission history of depression.

```{r rbans_results_12, results = "asis"}
print_html(rbans_ht_12)

```

## Depression vs Depression Scores after Hospitalization

```{r bdi_sparkline}
## -- Sparkline to show distribution of BDI at both time points ----------------
bdi_dist <- df_lt_base %>%
  filter(!is.na(bdi.totscore)) %>%
  group_by(fu.period, bdi.totscore) %>%
  summarise(count = n())

spark_bdi_3 <- sparkline(
  filter(bdi_dist, fu.period == "3 Month") %>% pull(count),
  type = 'bar',
  barColor = "#117cad",
  elementId = "sparkline-bdi-3"
)

spark_bdi_12 <- sparkline(
  filter(bdi_dist, fu.period == "12 Month") %>% pull(count),
  type = 'bar',
  barColor = "#117cad",
  elementId = "sparkline-bdi-12"
)

```

Severity of depression is measured in our cohort using the BDI-II, which has an irregular distribution (3m: `r spark_bdi_3`; 12m: `r spark_bdi_12`). Therefore, we will use proportional odds logistic regression models for both 3- and 12-month followup to determine the association between a pre-admission reported history of depression and severity of depression after discharge.

As noted in the RBANS section, in all long-term models, we'll include patients who had any assessment data available at a given time point (even if the outcome of interest is missing).

```{r bdi_models, results = "hide"}
## -- Fit model ----------------------------------------------------------------
## Will use restricted cubic splines for nonlinear terms; replace most
## continuous variables' names with rcs(var, 3)
bdi_mod_vars <-
  str_replace(setdiff(ltci_vars, "bdi.totscore"), rcs_replace_regex, "rcs\\(\\1, 3\\)")

fit_bdi_mod <- function(df, aregobj){
  fit.mult.impute(
    as.formula(paste("bdi.totscore ~", paste(bdi_mod_vars, collapse = " + "))),
    data = df,
    xtrans = aregobj,
    fitter = lrm
  )
}

bdi_mod_3 <- fit_bdi_mod(df = df_lt_3, aregobj = lt_areg_3)
bdi_mod_12 <- fit_bdi_mod(df = df_lt_12, aregobj = lt_areg_12)

bdi_results_3 <- rms_model_results(bdi_mod_3, rndDigits = 2) %>%
  filter(is.na(as.numeric(label)))
bdi_results_12 <- rms_model_results(bdi_mod_12, rndDigits = 2) %>%
  filter(is.na(as.numeric(label)))

## Add column names manually - couldn't get huxtable to do this properly/quickly
bdi_colnames <- c("Variable", "Ref Level", "Comparison", "Odds Ratio (95% CI)",
                  "X^2^", "df", "P")
bdi_results_3 <- rbind(bdi_colnames, bdi_results_3)
bdi_results_12 <- rbind(bdi_colnames, bdi_results_12)

## Make huxtables
bdi_ht_3 <- make_modresults_ht(bdi_results_3)
bdi_ht_12 <- make_modresults_ht(bdi_results_12)

## Numbers for text statement
bdi_or_3 <- exp(coef(bdi_mod_3)["hx.depression=Has history"])
bdi_change_3 <- ifelse(bdi_or_3 < 1, 1 - (bdi_or_3 / 1), bdi_or_3 / 1)
bdi_orci_3 <- bdi_results_3[grep("^hx\\.depression", bdi_results_3$label), "est.ci"]

bdi_or_12 <- exp(coef(bdi_mod_12)["hx.depression=Has history"])
bdi_change_12 <- ifelse(bdi_or_12 < 1, 1 - (bdi_or_12 / 1), bdi_or_12 / 1)
bdi_orci_12 <- bdi_results_12[grep("^hx\\.depression", bdi_results_12$label), "est.ci"]

```

### Model Results, 3M

Compared to patients with no documented history of depression, patients with a pre-admission history of depression as ascertained by surrogate questionnaire have, on average, `r bdi_orci_3` times the odds of a higher BDI-II score three months after discharge after adjusting for potential confounders. This indicates that in our cohort, after taking into account other available covariates, survivors of critical illness with a pre-admission history of depression are more likely to have more severe depression three months after hospitalization.

```{r bdi_results_3, results = "asis"}
print_html(bdi_ht_3)

```

### Model Results, 12M

Compared to patients with no documented history of depression, patients with a pre-admission history of depression as ascertained by surrogate questionnaire have, on average, `r bdi_orci_12` times the odds of a higher BDI-II score twelve months after discharge after adjusting for potential confounders. This indicates that in our cohort, after taking into account other available covariates, survivors of critical illness with a pre-admission history of depression are more likely to have more severe depression a year after hospitalization.

```{r bdi_results_12, results = "asis"}
print_html(bdi_ht_12)

```
